---
title: "R Markdown Primer"
author: "Tobias Lochner"
date: "2025-11-16"
output: html_document
---

# Introduction 

R Markdown is a framework that allows for the creation of documents such as PDFs and htmls. Within these documents users can blend text with executable R code. 

# Narrative

Doing this assignment has shown the benefits of being able to use R Markdown. Not only can we easily run and execute R code just like we can with an R script, we can also include plain text that allows us to tell a story with our data. Along with this R Markdown allows us to output this document that combines both R code and text in easy to read file formats such as html, pdf, or word. 

# LaTeX Expression 

The Pythagorean Theorem is $C^2 = A^2 + B^2$


```{r}
# 1st R Chunk

head(iris)

```

```{r}
# 2nd R Chunk

hist(iris$Sepal.Length)

```

# Conclusion 

I've used R Markdown in several classes before this, and it makes creating any sort of report that involves code very easy. I also think it's quite useful in school since it allows instructors to create Rmd files that include instructions and allow you to input the needed code. Like filling out a worksheet. 
